Vragenlijst thesis evaluatie

### 2015-08-09 doc/template/chap-5.tex
vanalles veranderd

One of the assumptions underlying game theory is that the players of the game are independent and self-interested. This does not necessarily mean that they want to harm other agents or that they only care about themselves. 
%utility function meaning 
Instead it means that each agent has preferences about which states of the world he likes. These preferences are mapped to natural numbers and are called the utility functions. The numbers are interpreted as a mathematical measure that tells how much an agent likes or dislikes the states of the world. \\
%Cooperative and non cooperative games
%-Remark- Stuk herschrijven-- Payoff introduceren -- zin van wikipedia
%Binnen de speltheorie is een 'spel' een (model van) interactie tussen spelers die individueel beslissingen nemen. De spelers ontvangen een beloning (pay-off) die afhangt van hun eigen beslissingen maar ook van die van de anderen. De volgende typen kunnen worden onderscheiden.
%
%Coöperatieve spellen en niet-coöperatieve spellen[bewerken]
%Het verschil tussen deze twee typen spellen is dat bij coöperatieve spellen (cooperative game theory) bindende afspraken tussen de spelers gemaakt kunnen worden terwijl dit niet mogelijk is bij de niet-coöperatieve spellen (non-cooperative game theory).

In a decision game-theoretic approach an agent will try to act in such a way as to maximize his expected or average utility function. It becomes more complicated when two or more agents want to maximise their utility and when actions of an agent can affect other agents' utilities. In this kind of game, the basic modelling unit is the group of agents. It is referred to as \textit{non-cooperative game theory}. In the individualistic approach the basic modelling is only one agent. This type of game is referred to as \textit{cooperative game theory}.

@@

An example to explain a Nash equilibrium of a two-player game is the prison dilemma. In this game there are two players who are both rational and both of them have committed a crime. `Rational' means that they want the best for themselves and it is not their purpose to do harm to others. Both are locked in a separate room and they cannot tell in advance to each other what they are going to say. Each of them can betray the other or they can support each other and remain silent. If a player confesses, he will either be imprisoned for 3 years or go free, depending on whether the other confesses. If the player is silent, he will either be imprisoned for 5 years or one year, depending on whether the other confesses.  \\ \todo{nakijken met praten, bekennen of andere veraden?}

@@

Figure \ref{Prison} shows the rewards of the possible actions of the two players. The figure shows that it is advantageous for each player to confess. If prisoner 1 talks and the other prisoner remains silent, prisoner 1 will be free. If prisoner 1 remains silent and the other prisoner talks, prisoner 1 gets five years in prison. If the prisoners cooperate and talk, both of them get three years in prison. If they both remain silent they will both get one year in prison. So this means that talking is the dominant strategy. A dominant strategy is a strategy that is better than all other strategies regardless of what the opponent does. The Nash equilibrium of the game is that they both confess even though it would be better if both prisoners cooperated and choose to stay silent.

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.6]{Images/PrisDilemma}
\caption{Prisoners dilemma: An example from the field of Game Theory. It is a game between two perfectly rational prisoners who do not know what the other one will do. Each prisoner can confess or stay silent. The resulting sentence is shown below each prisoner. }
\label{Prison}
\end{figure}

@@

If there is no feedback for either player, he will play in the same manner against every opponent. The strategy is then called \textit{non-adaptive} because the playing strategy is not dependent on the opponent's movements. An interesting subclass of the non-adaptive strategies is the one where the time intervals between two consecutive moves are generated by a renewal process \todo{renewal beter uitleggen}. An example of such renewal strategy is the periodic strategy where the time between two consecutive moves of the players is a fixed interval. An exponential strategy is a renewal strategy in which the interval between two consecutive moves is exponentially distributed. \\

@@

\subsubsection{Results of the FlipIt game}
The study of the different strategies by means of FlipIt framework allows to derive a number of interesting results \cite{FlipIt}:  
\begin{itemize}
\item periodic strategy strongly dominates the other renewal strategies if the opponent has a periodic or non-arithmetic renewal strategy. This means that it is always advantageous for the opponent to play periodically against a player with a non-adaptive strategy;
\item periodic games are disadvantageous against players following a Last Move adaptive strategy;
\item if a defender facing an LM attacker and with a cost much lower than the attacker, he can play with a periodic rate that is fast enough he'll force the attacker to drop out;
\item a defender facing an LM attacker has to play with a randomized strategy e.g. exponential strategy;
%-Remark- Matthias: Hoe is ‘exponential strategy’ randomized? En uitgebreider spreken over de condities: een defender facing an LM attacker and comparable cost…
\item any amount of feedback about the opponent received during the game, benefits to a player.
\end{itemize}
%-Remark- Matthias: Wat is ‘benefits the player’? Als de speler de feedback negeert benefit die info de speler niet. Ik zou zeggen ‘any amount of feedback about the opponent received during the game allows for better strategies/leads to a better strategy’ ofzo. Let op: Dit is een sterkere/straffere uitspraak, dus denk hier wel goed over na natuurlijk!

>>>>

One of the assumptions underlying game theory is that the players of the game are independent and self-interested. This does not necessarily mean that they want to harm other agents or that they only care about themselves. 
%utility function meaning 
Instead it means that each agent has preferences about which states of the world he likes. These preferences are mapped to natural numbers and are called the utility functions. The numbers are interpreted as a mathematical measure that tells how much an agent likes or dislikes the states of the world. \\
%Cooperative and non cooperative games
%-Remark- Stuk herschrijven-- Payoff introduceren -- zin van wikipedia
%Binnen de speltheorie is een 'spel' een (model van) interactie tussen spelers die individueel beslissingen nemen. De spelers ontvangen een beloning (pay-off) die afhangt van hun eigen beslissingen maar ook van die van de anderen. De volgende typen kunnen worden onderscheiden.
%
%Coöperatieve spellen en niet-coöperatieve spellen[bewerken]
%Het verschil tussen deze twee typen spellen is dat bij coöperatieve spellen (cooperative game theory) bindende afspraken tussen de spelers gemaakt kunnen worden terwijl dit niet mogelijk is bij de niet-coöperatieve spellen (non-cooperative game theory).
The choices of each agent produce an outcome, with respect to the utilities of the agent. A pay-off of an agent is the 
Games can be devised into two types of games: cooperative or non-cooperative. In a non cooperative game, the basic modelling unit is the group of agents. 
Two or more agents want to maximise their utility and their actions can be affected by other agents' utilities. In the individualistic approach the basic modelling is only one agent. This type of game is referred to as \textit{cooperative game theory}.

@@

An example to explain a Nash equilibrium of a two-player game is the prison dilemma. In this game there are two players who are both rational and both of them have committed a crime. `Rational' means that they want the best for themselves and it is not their purpose to do harm to others. Both are locked in a separate room and they cannot tell in advance to each other what they are going to say. Each of them can betray the other or they can support each other and remain silent. If a player talks, he will either be imprisoned for 3 years or go free, depending on whether the other talks. If the player is silent, he will either be imprisoned for 5 years or one year, depending on whether the other talks.

@@

Figure \ref{Prison} shows the rewards of the possible actions of the two players. The figure shows that it is advantageous for each player to talk (betraying the other). If prisoner 1 talks and the other prisoner remains silent, prisoner 1 will be free. If prisoner 1 remains silent and the other prisoner talks, prisoner 1 gets five years in prison. If the prisoners cooperate and talk, both of them get three years in prison. If they both remain silent they will both get one year in prison. So this means that talking is the dominant strategy. A dominant strategy is a strategy that is better than all other strategies regardless of what the opponent does. The Nash equilibrium of the game is that they both talk even though it would be better if both prisoners cooperated and choose to stay silent.

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.6]{Images/PrisDilemma}
\caption{Prisoners dilemma: An example from the field of Game Theory. It is a game between two perfectly rational prisoners who do not know what the other one will do. Each prisoner can talk (betraying the other) or remain silent. The resulting sentence is shown below each prisoner. }
\label{Prison}
\end{figure}

@@

If there is no feedback for either player, he will play in the same manner against every opponent. The strategy is then called \textit{non-adaptive} because the playing strategy is not dependent on the opponent's movements. An interesting subclass of the non-adaptive strategies are the Renewal strategies where the time intervals between two consecutive moves are generated by a renewal process. The length between two consecutive moves are independent and identically distributed random variables chosen from a density formula \textit{f}. This renewal process means that the strategies are renewed after each move: the interval until the next move only depends on the current move time and not on previous history. \todo{check comment in latex}
%-Remark- Vorige zin is gecopypaste van FlipIt
An example of such renewal strategy is the periodic strategy where the time between two consecutive moves of the players is a fixed interval. An exponential strategy is a renewal strategy in which the interval between two consecutive moves is exponentially distributed. \\

@@

\subsubsection{Results of the FlipIt game}
The study of the different strategies by means of FlipIt framework allows to derive a number of interesting results \cite{FlipIt}:  
\begin{itemize}
\item periodic strategy strongly dominates the other renewal strategies if the opponent has a periodic or non-arithmetic renewal strategy. This means that it is a good choice for the opponent to play periodically against a player with a non-adaptive strategy;
\item periodic games are disadvantageous against players following a Last Move adaptive strategy. The opponent can observe the exact time of the player's next move and play immediately afterwards. If the costs are from the same magnitude, the opponent can keep the control over the resource with little interrupts from the other player; 
\item a player facing an LM opponent and with a cost much lower than the opponent has two options. The first option is to move with a periodic rate that is fast enough he'll force the opponent to drop out. The other option is to play with a randomized strategy, such that the opponent cannot learn any information regarding the next move of the player;
\item the best defence strategy is to play fast, to make the opponent drop out of the game. To be able to move fast, the player has to make sure that the cost of moving is much less than the opponents moves.
%-Remark- Matthias: Hoe is ‘exponential strategy’ randomized? En uitgebreider spreken over de condities: een defender facing an LM attacker and comparable cost…
%\item any amount of feedback about the opponent received during the game, benefits to a player.
\end{itemize}
%-Remark- Matthias: Wat is ‘benefits the player’? Als de speler de feedback negeert benefit die info de speler niet. Ik zou zeggen ‘any amount of feedback about the opponent received during the game allows for better strategies/leads to a better strategy’ ofzo. Let op: Dit is een sterkere/straffere uitspraak, dus denk hier wel goed over na natuurlijk!
